UKB Simulation Analyses

### 2023-12-14 ohbm_results.Rmd

ggsave("figs/male_variance_ohbm_big.jpeg", p_annotate, width=7, height=8)
```
# Replication

```{r}
permutation_path <- "/Users/megardn/Desktop/BGD_Repos/combat_biovar/ukb_perm_csvs"
```

>>>>

ggsave("figs/male_variance_ohbm_big.jpeg", p_annotate, width=7, height=8)
```
# Replication 
Permuting site assignments 3x

```{r}
#path to csvs scp'd from cubic
permutation_path <- "/Users/megardn/Desktop/BGD_Repos/combat_biovar/derivatives/ukb_perm_csvs"
```

### 2023-12-14 paper_figs.Rmd

#ukb data from ohbm_results.Rmd
cent_err.p <- readRDS("data/ukb_perm_csvs/centile_errors.RDS")
z_diffs2 <- readRDS("ukb_basic/z_diffs.RDS")
cent.diffs3 <- readRDS("ukb_basic/cent_diffs.RDS")
ukb_data <- fread("data/ukb_to_model/ukb_CN_data_simsites.csv")
#cent_abs.diffs <- readRDS("data/centile_abs_diffs.rds")
```

>>>>

#ukb data from ohbm_results.Rmd
cent_err.p <- readRDS("derivatives/ukb_perm_csvs/centile_errors.RDS")
z_diffs2 <- readRDS("ukb_basic/z_diffs.RDS")
cent.diffs3 <- readRDS("ukb_basic/cent_diffs.RDS")
ukb_data <- fread("data/ukb_to_model/ukb_CN_data_simsites.csv")
#cent_abs.diffs <- readRDS("data/centile_abs_diffs.rds")
```

### 2023-12-14 ukb_sim.site_analyses.Rmd

>>>>

## Varying M:F

Visualize simulated sites (`scp -r 'gardnerm@cubic-login.uphs.upenn.edu:/cbica/home/gardnerm/combat-biovar/data/ukb_ratios/*.csv' ./data/ukb_ratios/`)

```{r}
ratio_data_path <- "/Users/megardn/Desktop/BGD_Repos/combat_biovar/data/ukb_ratios"
raw_files <- list.files(path = ratio_data_path, pattern = "_raw.csv", full.names = TRUE)

df <- data.frame() #new empty dataframe
for (file in raw_files) {
  # Read each CSV file
    data <- fread(file)

    # Add a "Source_File" column with the file name
    data <- data %>%
      dplyr::select(c(sim.site, participant, sex, site, age_days)) %>%
      mutate(Source_File = as.factor(basename(file))) %>%
      mutate(dataset = gsub("_data|_raw.csv|prop-|[0-9]|-", "", Source_File))

    # Bind the data to the combined dataframe
    df <- bind_rows(df, data, .id = "File_ID")
    assign("ratio_sites", df)
}
length(unique(ratio_sites$Source_File))
```

```{r}
ggplot(ratio_sites) +
  geom_bar(aes(x=sim.site, fill=sex), position = "fill") +
  scale_y_continuous(name = "percent",
                     breaks = seq(0, 1, by=0.1), 
                     labels = scales::percent(seq(0, 1, by=0.1))) +
  facet_wrap(~Source_File)
```

```{r}
ggplot(ratio_sites) +
  geom_histogram(aes(x=age_days, fill=sim.site), position = "identity", alpha=0.4, binwidth = 365) +
  facet_wrap(~Source_File)

ggplot(ratio_sites) +
  geom_histogram(aes(x=age_days, fill=Source_File, color=Source_File), position = "identity", alpha=0.4, binwidth = 365)
```

```{r}
#path to csvs scp'd from cubic
ratio_path <- "/Users/megardn/Desktop/BGD_Repos/combat_biovar/derivatives/ukb_ratio"
```

### Centiles
Do centile scores change based on combat version?

```{r}
n_ratio_list <- lapply(c(1:11), str_pad, 2, pad = "0")
n_ratio_list <- paste0("prop-", n_ratio_list)
pheno_list.z <- paste0(pheno_list, ".z")

# combined_preds.p <- data.frame()
get.predictions.ratio <- function(x){
  df <- data.frame() #new empty dataframe
  pred.csvs.p <- list.files(path = ratio_path, pattern = paste0(x, ".+_predictions.csv"), full.names = TRUE)
  for (file in pred.csvs.p) {
    # Read each CSV file
    data <- fread(file)

    # Add a "Source_File" column with the file name
    data <- data %>%
      mutate(Source_File = as.factor(basename(file)),
             perm = as.factor(x)) %>%
      mutate(dataset = gsub("_data|_predictions.csv|prop-|[0-9]|-", "", Source_File))

    # Bind the data to the combined dataframe
    df <- bind_rows(df, data, .id = "File_ID")
  }
  return(df)
}
ratio_predictions <- mclapply(n_ratio_list, get.predictions.ratio, mc.preschedule = FALSE)
```
